Spatial Reasoning and Data Displays

### 2015-01-19 Paper/Draft1/TestingVisualAptitude.Rnw
PC discussion
Demographic factors re-phrasing

\comment{add something about x and y axis in the description of the figure. }
\newtext{Figure \ref{fig:lineupblockpca} shows the relative contribution each input variable makes to each principal component, weighted by the importance of each PC. This allows us to consider the rotation matrix visually; for instance, we see that again, PC1 accounts for most of the variance and seems to represent general visual aptitude. }
% PC2 emphasizes the relationship between figure classification and lineup task 1 (and to a lesser extent, on lineup task 2). PC3 differentiates the lineup task 3 from the visual search task; other tasks do not impact PC3 to a meaningful degree. PC4 separates lineup test 2 from the paper folding and card rotation tests and emphasizes the overlap with the visual search test. PC5 separates lineup test 2 and the figure classification test from the overlap between the other lineup tests and the visual search test. PC6 and PC7 account for a joint total of less than 10\% of the overall variability, and do not display any distinct patterns in the loadings.
%
PC2 emphasizes the overlapping variation in performance on lineup test 1 and the figure classification test. PC3 emphasizes the additional variation in performance on lineup test 3 and the visual search test, while PC4 emphasizes the extra variability in performance on lineup test 2 and the paper folding test. All three lineups, plus the figure classification, paper folding, and visual search tests contribute to PC5. PC6 and PC7 jointly account for less than 10\% of the variance in the data and do not display any distinct patterns in the loadings. 
%\Sexpr{as.numeric(round(100*importance[6], 1))}\% and \Sexpr{as.numeric(round(100*importance[7], 1))}\% of the variance, respectively; PC6 seems to differentiate the first two lineup tasks from the overlap between the third lineup task and the figure classification task.

@@

Performance on lineups is strongly related to performance on tests of visual ability; however, this relationship is mediated by demographic factors such as major (STEM or not) and completion of calculus I.
In addition to these demographic factors, many facets of intelligence are highly correlated; those who score higher on general aptitude tests may score higher on tests of visual ability (and may also score higher on lineup tests).

\comment{reference is gone astray `those who score' ... the previous subject were facets of intelligence, and they do not score on tests - what you mean are people, so say that!}

>>>>

% \comment{add something about x and y axis in the description of the figure. }
\newtext{Figure \ref{fig:lineupblockpca} shows the relative contribution each input variable makes to each principal component, weighted by the importance of each PC. The input variables are shown on the $y$ axis, with the importance to each PC shown on the $x$ axis. This allows us to consider the rotation matrix visually; for instance, we see that again, PC1 accounts for most of the variance and seems to represent general visual aptitude. }
% PC2 emphasizes the relationship between figure classification and lineup task 1 (and to a lesser extent, on lineup task 2). PC3 differentiates the lineup task 3 from the visual search task; other tasks do not impact PC3 to a meaningful degree. PC4 separates lineup test 2 from the paper folding and card rotation tests and emphasizes the overlap with the visual search test. PC5 separates lineup test 2 and the figure classification test from the overlap between the other lineup tests and the visual search test. PC6 and PC7 account for a joint total of less than 10\% of the overall variability, and do not display any distinct patterns in the loadings.
%
PC2 emphasizes the overlapping variation in performance on lineup test 1 and the figure classification test. PC3 emphasizes the additional variation in performance on lineup test 3 and the visual search test, while PC4 emphasizes the extra variability in performance on lineup test 2 and the paper folding test. All three lineups, plus the figure classification, paper folding, and visual search tests contribute to PC5. PC6 and PC7 jointly account for less than 10\% of the variance in the data and do not display any distinct patterns in the loadings. 
%\Sexpr{as.numeric(round(100*importance[6], 1))}\% and \Sexpr{as.numeric(round(100*importance[7], 1))}\% of the variance, respectively; PC6 seems to differentiate the first two lineup tasks from the overlap between the third lineup task and the figure classification task.

@@

Performance on lineups is strongly related to performance on tests of visual ability; however, this relationship is mediated by demographic factors such as major (STEM or not) and completion of calculus I.
In addition to these demographic factors, many facets of intelligence are highly correlated; participants who score higher on general aptitude tests may score higher on tests of visual ability (and may also score higher on lineup tests).

% \comment{reference is gone astray `those who score' ... the previous subject were facets of intelligence, and they do not score on tests - what you mean are people, so say that!}
